Probability Aggregation: Dynamic Hierarchical Modeling of Expert Beliefs in Geopolitical Events

### 2013-08-26 paper.tex
Edits

\section{Introduction}
\label{intro}
Individual experts can differ radically from one another in their abilities to assess probabilities of future events. The quality of a probability assessment is typically evaluated in regards to \textit{calibration} that measures the degree to which the frequency of occurrence of the events agree with the given probabilities. This means that, for instance, the proportion of events that actually occurred is 60\% for all those events for which a well-calibrated expert assessed a probability of 0.60. Unfortunately, several experiments have been conducted to show that experts are generally poorly calibrated (see, e.g., \citet{cooke1991experts, shlyakhter1994quantifying}). \citet{wright1994coherence}, however, argue that a higher level of self-reported expertise on the subject-matter can be associated with better calibration.

@@

\subsection{In- and Out-of-Sample Sharpness and Calibration}
\label{calibration}
A calibration plot is a simple tool for assessing the sharpness and calibration of a model. The idea is to plot the probability forecasts against the observed empirical frequencies. Any deviation from the diagonal line therefore suggests poor calibration. A model is considered under-confident (or over-confidence) if the points follow an S-shaped (or \reflectbox{S}-shaped) trend. In order to assess sharpness of the model, it is common practice to place a histogram of the given forecasts in the corner of the plot.

>>>>

\section{Introduction}
\label{intro}
Individual experts can differ radically from one another in their abilities to assess probabilities of future events. The quality of a probability assessment is typically evaluated in regards to \textit{calibration}, which is an attribute measuring the degree to which the frequency of occurrence of the events agree with the given probabilities. This means that, for instance, the proportion of occurred events is 60\% for all those events for which a well-calibrated expert assessed a probability of 0.60. Even though several experiments have been conducted to show that experts are generally poorly calibrated (see, e.g., \citet{cooke1991experts, shlyakhter1994quantifying}), relative differences can occur between different types of experts. In particular, \citet{wright1994coherence} argue that a higher level of self-reported expertise on the subject-matter can be associated with better calibration.

@@

\subsection{In- and Out-of-Sample Sharpness and Calibration}
\label{calibration}
A calibration plot is a simple tool for assessing the sharpness and calibration of a model. The idea is to plot the probability forecasts against the observed empirical frequencies. Any deviation from the diagonal line therefore suggests poor calibration. A model is considered under-confident (or over-confidence) if the points follow an S-shaped (or \reflectbox{S}-shaped) trend. In order to assess sharpness of the model, it is common practice to place a histogram of the given forecasts in the corner of the plot. Since the data were balanced, any deviation from the the baseline probability at 0.5 suggests improved sharpness.
